Peripheral Edema measurement methods (by ArticleAggregator_v03)

### 2022-11-08 ArticleAggregator_v05_pure.qmd
Article Aggreagor PubMed Term added

```{r}
#| label: Environment Setup
final_col_names <- c("Title", "Author", "Year", "FTlink", "Src", "Info", "PubDate", "PubType", "Abstract", "CT",      "PMID", "PUI", "DOI", "EBlink", "OpenLink") 
term <- "'peripheral edema' measurement"
aa_path <- r"(C:\Users\I0172484\Documents\03 - Scripts\R\WebScrap\ArticleAggregator_data\)"
# setwd(aa_path)
```

@@

```{r}
#| label: Load Google Scholar page
gs_term <- str_replace_all(term, " ", "+")
my_uri <- glue("https://scholar.google.com/scholar?hl=en&as_sdt=0%2C5&q={gs_term}")
gs <- read_html(my_uri)
n_hits <- gs %>% html_elements("#gs_ab_md .gs_ab_mdw") %>% html_text() %>% str_extract("\\d+") %>% as.integer()
n_pg <- n_hits %/% 10 + 1
# n_pg <- gs %>% html_elements("#gs_n a") %>% html_text() %>% as.integer() %>% na.omit() %>% max()

@@

## Manually input missing values ;)
```
## Pubmed
```{r}
#| label: PubMed connection and article extraction
api_key <- "0b1204719f054732c66e608d9d3f2c749c08"
pm_query <- "peripheral[tiab] edema[tiab] measurement[tiab]"
# pm_query <- glue("{term}[tiab]")
my_entrez_id <- get_pubmed_ids(pm_query, api_key=api_key)
my_entrez_id$QueryTranslation
my_entrez_id$Count

>>>>

```{r}
#| label: Environment Setup
final_col_names <- c("Title", "Author", "Year", "FTlink", "Src", "Info", "PubDate", "PubType", "Abstract", "CT",      "PMID", "PUI", "DOI", "EBlink", "OpenLink") 
term <- "peripheral edema measurement"
aa_path <- r"(C:\Users\I0172484\Documents\03 - Scripts\R\WebScrap\ArticleAggregator_data\)"
# setwd(aa_path)
```

@@

```{r}
#| label: Load Google Scholar page
gs_term <- str_replace_all(term, " ", "+")
# my_uri <- glue("https://scholar.google.com/scholar?hl=en&as_sdt=0%2C5&q={gs_term}")

# For Title; including patents; excluding citation
my_uri <- glue("https://scholar.google.com/scholar?hl=en&as_sdt=2007&as_vis=1&q=allintitle%3A+{gs_term}&btnG=")

gs <- read_html(my_uri)
n_hits <- gs %>% html_elements("#gs_ab_md .gs_ab_mdw") %>% html_text() %>% str_extract("\\d+") %>% as.integer()
n_pg <- n_hits %/% 10 + 1
# n_pg <- gs %>% html_elements("#gs_n a") %>% html_text() %>% as.integer() %>% na.omit() %>% max()

@@

## Manually input missing values ;)
```
## Pubmed
```{r}
#| label: PubMed connection and article extraction
api_key <- "0b1204719f054732c66e608d9d3f2c749c08"

sl_term <- str_split(term, " ", simplify=TRUE)
pm_query <- str_c(sl_term,"[tiab] ", collapse="")

# pm_query <- "peripheral[tiab] edema[tiab] measurement[tiab]"
# pm_query <- glue("{term}[tiab]")

my_entrez_id <- get_pubmed_ids(pm_query, api_key=api_key)
my_entrez_id$QueryTranslation
my_entrez_id$Count
